%================ch1======================================
\chapter{Introduction}\label{ch:ch1}

\section{Gaia Mission}
We have come a long way in observing the skies, from the naked eye to the mural instrument, from telescopes to space missions. The Gaia mission \citep{gaia} \citep{gaiafaccs} is one such astrometry mission launched in 2013. The spacecraft aims to measure the positions, distances and motions of celestial objects. The mission aims to be the most precise 3D catalogue of the sky, mapping every object it can while also measuring their motions which can give clues about the origin and evolution of our galaxy, the Milky Way.

The mission aims to determine the position and parallax of around a billion stars to an accuracy of around 20 $\mathrm{\mu}$as. The catalogue is set to be released in stages. The first data release took place in 2016 \citep{gaiadr1}, based on 14 months of observation. It inlcuded the positions and magnitudes for over a billion stars using only Gaia data. The second data release took place in 2018 \citep{gaiadr2}, after 22 months of observations, and improved on the precision of the previous release, as well as adding parallaxes and proper motions.

\section{Star Clusters}
Gravity is one of the 4 fundamental forces which keeps large celestial structures in place. A star cluster is a gravitationally bound group of stars. They can be globular or open.

\subsection{Globular Clusters}
A globular cluster is a roughly spherical collection of stars orbiting the galactic core. They are composed of thousands of low metal stars. They are generally found in the halo of a galaxy and are generally older than the stars in open clusters \citep{globclust}. The proportion of metals, called metallicity, is rather low in these stars. The metallicity of a star is an indicator of its age, and the low metallicity of stars in globular clusters shows this \citep{introstars}.

\subsection{Open Clusters}
An open cluster is a group of a few thousand stars formed from the same molecular cloud. They are loosely bound by gravitational attraction and are generally found in the disc of the galaxy. Properties of the cluster members can be determined easily because they have are at the same distance away from us and they have a similar age and chemical composition \citep{openclust}. This will also be the focus of this report.

\section{Gaia Data for Open Clusters}
While the Gaia mission provided us with very precise data regarding astronomical objects, they do not come classified. The study by Cantat-Gaudin et. al \citep{cg} aims to determine a list of members of open clusters and derive mean parameters from them using Gaia data. They obtained a list of 1229 open clusters with associated members and cluster parameters. The cluster members identified by Cantat-Gaudin are available on the VizieR database \citep{vizier}, which is used for this study. The data lists the positions of the clusters and their members, with parallaxes, proper motions and color magnitudes. From the other Gaia data, other information can also be queried for individual stars. Combining the data, the properties of these star clusters can be studied. Eventually, we can separate the binary stars from the single ones and study their radial distributions. We can then examine their evolution and morphology.



